---
title: "Interactive Plot as an HTML object (similar to D3.js)"
subtitle: "Daily Price Change Index (%) of Laptop Using Web-Scraped Amazon Data"
author: Harold Gomes
output: html_notebook
fig_width: 8
fig_height: 6
---





### R package to convert into JavaScript style plot, embedded into HTML 
I did an independent research to investigate whether there is any R package that would convert R plots into HTML interactive object and would work with R-Markdown. Surprise! I found `library(dygraphs)` that could plot a time series object (`.xts`) into Java script style data visual products. Currently it can only handle time series plots and no other types of plot. 
https://rstudio.github.io/dygraphs/index.html

### Prototype Development
Here I am developing a prototype that could display the Price Chance Index to the users and stakeholders. Hence, I could share this as a HTML object to my clients. It gives the ability for interactive plotting, inspect point values by hovering around the data point, and change the axis to the users.  


### Load Data
```{r}
load('S:/SURV727_Fundamental_Computing_DataDisplay/Final_Project/Amazon/Data/data_index.Rda')
head(data_index)
```


### Load R Package
```{r}
library(xts) ## convert dataframe to timeseries object
library(tidyverse)
library(dygraphs)  ## Java script style data visuals 
```


### Load data and re-structure
```{r}
df0 <- data_index %>%
  filter(., IX_type=="Proxy_wgt") %>%
  select(., Date1, L_IX, P_IX, G_IX, F_IX, T_IX, Unwgt_IX)

df1 <- data_index %>%
  filter(., IX_type=="Popularity_Adj_Proxy_wgt") %>%
  select(., Date1, L_IX, P_IX, G_IX, F_IX, T_IX, Unwgt_IX) %>%
  rename(., L_IX_adj=L_IX, P_IX_adj=P_IX, G_IX_adj=G_IX, F_IX_adj=F_IX, T_IX_adj=T_IX, Unwgt_IX_adj=Unwgt_IX)
```


### Convert datafreame into a timeseries object class (.xts). 
### Merge multiple timeseries objects
https://cran.r-project.org/web/packages/tsbox/vignettes/tsbox.html
https://rstudio-pubs-static.s3.amazonaws.com/40873_5fbe3860854a47c38a58aabd01f9cf9d.html

```{r}
df_proxy <- xts(df0[, -1], df0[, 1])
head(df_proxy, 5) 

df_pop_adj <- xts(df1[, -1], df1[, 1])
head(df_pop_adj, 5) 

# Merge 2 TS object into one object
df_all <- merge(df_proxy, df_pop_adj)
head(df_all, 5) 
```


## Plotting Index Data
Next few graphs display the data and presented in various ways.

### User may hover around the datapoints and change the x and y axis by selecting and dragging with the mouse, or with the slider (when available).

### Graph1: Basic Plot
```{r, fig.width=8, fig.height=4}
dygraph(df_proxy)
```


### Graph 2: Basic Plot with Slider
```{r, fig.width=8, fig.height=4}
dygraph(df_proxy) %>% dyRangeSelector()
```


### Graph3: Change labels of the legend
Laspeyres, Paasche, Geo-means, Tornqvist, Fisher, Unweighted, and Average Price
```{r, fig.width=8, fig.height=4}
dygraph(df_proxy) %>%
  dySeries("L_IX", label = "Laspeyres") %>%
  dySeries("P_IX", label = "Paasche") %>%
  dySeries("G_IX", label = "Geo-means") %>%
  dySeries("T_IX", label = "Tornqvist") %>%
  dySeries("F_IX", label = "Fisher") %>%
   dySeries("Unwgt_IX", label = "Unweighted") %>%
  dyOptions(stackedGraph = FALSE) %>%
  dyRangeSelector(height = 20)
```


### Graph4: Customize colors with RColorBrewer. Add Title
```{r, fig.width=8, fig.height=4}
dygraph(df_proxy, main = "Daily Laptop Index from Amazon Data (Top 100 Best)") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(6, "Set2")) %>%
  dyRangeSelector(height = 20) %>%
  
  dySeries("L_IX", label = "Laspeyres") %>%
  dySeries("P_IX", label = "Paasche") %>%
  dySeries("G_IX", label = "Geo-means") %>%
  dySeries("T_IX", label = "Tornqvist") %>%
  dySeries("F_IX", label = "Fisher") %>%
  dySeries("Unwgt_IX", label = "Unweighted") %>%
dyOptions(colors = RColorBrewer::brewer.pal(6, "Set3"))

# "dot" (default), "triangle", "square", "diamond", "pentagon", "hexagon", "circle", "star", "plus" or "ex"
```


### Graph5: Display points
```{r, fig.width=8, fig.height=4}
dygraph(df_proxy, main = "Daily Laptop Index from Amazon Data (Top 100 Best)") %>%
  dySeries("L_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
           label = "Laspeyres", color = "blue") %>%
  dySeries("P_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
           label = "Paasche", color = "red") %>%
  
  dySeries("G_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
           label = "Geo-means") %>%
  dySeries("T_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
           label = "Tornqvist") %>%
  dySeries("F_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
           label = "Fisher") %>%
   dySeries("Unwgt_IX", drawPoints = TRUE, pointShape = "triangle", pointSize=4,
            label = "Unweighted") %>%
  dyRangeSelector(height = 20) 

# "dot" (default), "triangle", "square", "diamond", "pentagon", "hexagon", "circle", "star", "plus" or "ex"
 
 #dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))

```



The End.






