---
title: "Step 2: Matched Samples.Compute Index"
subtitle: "Harold Gomes"
author: ""
output: #html_notebook
---



```{r}
library(tidyverse)

```


### Base Price (Previous)
```{r}
load('S:/SURV727_Fundamental_Computing_DataDisplay/Final_Project/Amazon/Data/2019-10-30_2.rda')
base_price <- pop2 %>%  drop_na(.)
names(base_price) <- c("Rank0", "Product_Name", "Rating0" ,"Count_Review0", "Price0", "Date0", "Day0")
base_price
```

### Current Price
```{r}
load('S:/SURV727_Fundamental_Computing_DataDisplay/Final_Project/Amazon/Data/2019-10-31_1.rda')
current_price <- pop2 %>%  drop_na(.)
names(current_price) <- c("Rank1", "Product_Name", "Rating1", "Count_Review1", "Price1", "Date1", "Day1")
current_price
```


### Inner join 2 datasets to keep the Matched Samples

```{r}
options(scipen = 999)
df_join <- inner_join(current_price, base_price, by = "Product_Name") %>% 
  ### Calculate Price change for Each Laptop ###
  mutate(., PriceChange = Price1 - Price0,
         PriceChange_prct = (Price1 - Price0)*100/Price0,
         PriceChange_prct = round(PriceChange_prct, digits=2)) %>%
  select("Rank1","Rank0", "Product_Name", "Price1","Price0", "PriceChange", "PriceChange_prct", "Count_Review1","Count_Review0","Rating1", "Rating0","Date1","Date0","Day1","Day0") %>%
  drop_na(.)
df_join

### Matched Sample Size out of Top 100 laptops ###
nrow(df_join)
```


### Check total Price and pseudo weights to assees how much changed

```{r}
rbind(sum(df_join$Price1),
sum(df_join$Price0),
sum(df_join$Count_Review0),
sum(df_join$Count_Review1),
sum(df_join$Price1) - sum(df_join$Price0))
```

### Create Popularity Adjusted Proxy Weight based on Dr. Kern’s Suggestion.
#### Use suvery design methodology to construct an adjutment factor, calibration factor between sample total into population total, then compute the popularity-adjusted-review (Adj_wgt1, Adj_wgt0)

```{r}
options(scipen = 999)

df <- df_join %>% 
  ### Construct Adjustement Factor and  ###
  mutate(., Adj_fct1 = Rating1/5,
         Adj_fct0 = Rating0/5,
         
         Adj_wgt1_sample = Adj_fct1*Count_Review1,
         Adj_wgt0_sample = Adj_fct0*Count_Review0) %>% 
  
  ### Construct Calibration Factor ###
  mutate(.,  Calibration_fct1 = sum(Count_Review1) /sum(Adj_wgt1_sample),
         Calibration_fct0 = sum(Count_Review0) /sum(Adj_wgt0_sample)) %>% 
  
  ### Compute Popularity Adjusted Proxy Weight ###
         mutate(., Adj_wgt1 = round(Adj_wgt1_sample*Calibration_fct1, digits=0),
                Adj_wgt0 = round(Adj_wgt0_sample*Calibration_fct0, digits=0))
df


### Ascertain that totals match after calibration. Due to rounding, slight error possible ###
rbind(sum(df$Adj_wgt0),
sum(df$Count_Review0),
sum(df$Adj_wgt1),
sum(df$Count_Review1))
```

### RUN ONLY for the BASE PERIOD
### `## Harold's Note ##`: Next step is to produce various types of index.

```{r}
df2 <- df %>% 
  rename(p0=Price0, q0=Count_Review0, p1=Price1, q1=Count_Review1)

###############################
### compute Index Relatives ###
###############################
Daily_IXrel <- df2  %>% 
  ### Laspeyres, Paasche Index ###
  mutate(., L_IXrel = 1,  
         P_IXrel = 1) %>%
  
  ### Geo-means Index ###
  mutate(., G_IXrel = 1) %>% 
  
  ### Tornqvist Index ###
  mutate(.,  T_IXrel = 1) %>% 
  
  ### Fisher Index ###
  mutate(., F_IXrel = 1) %>%
  
  ### Unwighted Price Index ###
  mutate(., Unwgt_IXrel = 1) %>%
  
  ### Average Price Index ###
  mutate(., AvePrc = round(mean(base_price$Price0), digits=2)) %>%
  select(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date0, Day0) %>%
  distinct(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date0, Day0)


#####################
### compute Index ###
#####################
Daily_IX_proxy <- Daily_IXrel %>%
  mutate(L_IX=round((L_IXrel-1)*100, digits=3), 
         P_IX=round((P_IXrel-1)*100, digits=3), 
         G_IX=round((G_IXrel-1)*100, digits=3),
         F_IX=round((F_IXrel-1)*100, digits=3),
         T_IX=round((T_IXrel-1)*100, digits=3),
         Unwgt_IX=round((Unwgt_IXrel-1)*100, digits=3),
         IX_type="Proxy_wgt", n_matched=100)

Daily_IX_Adj <- Daily_IXrel %>%
  mutate(L_IX=round((L_IXrel-1)*100, digits=3), 
         P_IX=round((P_IXrel-1)*100, digits=3), 
         G_IX=round((G_IXrel-1)*100, digits=3),
         F_IX=round((F_IXrel-1)*100, digits=3),
         T_IX=round((T_IXrel-1)*100, digits=3),
         Unwgt_IX=round((Unwgt_IXrel-1)*100, digits=3),
         IX_type="Popularity_Adj_Proxy_wgt", n_matched=100)

##############################
### Append 2 type of Index ###
##############################
Daily_IX_0 <- rbind(Daily_IX_proxy, Daily_IX_Adj) %>% 
  rename(Date1=Date0, Day1=Day0)
Daily_IX_0

```

### `## Harold's Note ##`: Next step is to produce various types of index.

## Compute Index: Laspeyres, Paasche, Geo-means, Tornqvist, Fisher, Unweighted, and Average Price
#### Using Tidyverse

```{r}
df2 <- df %>% 
  rename(p0=Price0, q0=Count_Review0, p1=Price1, q1=Count_Review1)

###############################
### compute Index Relatives ###
###############################
Daily_IXrel <- df2  %>% 
  ### Laspeyres, Paasche Index ###
  mutate(., L_IXrel = sum(q0*p1)/sum(q0*p0),  
         P_IXrel = sum(q1*p1)/sum(q1*p0)) %>%
  
  ### Geo-means Index ###
  mutate(., p1_over_p0 = p1/p0,
         p0q0 = p0*q0,
         s0 = p0q0 / sum(p0q0),
         G_IXrel = prod((p1_over_p0)^s0)) %>% 
  
  ### Tornqvist Index ###
  mutate(., p1q1 = p1*q1,
         s1 = p1q1 / sum(p1q1),
         T_IXrel = prod((p1_over_p0)^((s0+s1)/2))) %>% 
  
  ### Fisher Index ###
  mutate(., F_IXrel = sqrt(L_IXrel*P_IXrel)) %>%
  
  ### Unwighted Price Index ###
  mutate(., Unwgt_IXrel = sum(p1)/sum(p0)) %>%
  
  ### Average Price Index ###
  mutate(., AvePrc = round(mean(current_price$Price1), digits=2)) %>%
  select(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date1, Day1) %>%
  distinct(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date1, Day1)


#####################
### compute Index ###
#####################
Daily_IX_proxy <- Daily_IXrel %>%
  mutate(L_IX=round((L_IXrel-1)*100, digits=3), 
         P_IX=round((P_IXrel-1)*100, digits=3), 
         G_IX=round((G_IXrel-1)*100, digits=3),
         F_IX=round((F_IXrel-1)*100, digits=3),
         T_IX=round((T_IXrel-1)*100, digits=3),
         Unwgt_IX=round((Unwgt_IXrel-1)*100, digits=3),
         IX_type="Proxy_wgt", n_matched=nrow(df2))

```

### Popularity adjusted proxy weight. Re-run it to compute the index and append it to previous dataset
#### Using Tidyverse


```{r}
df2 <- df %>% 
  rename(p0=Price0, q0=Adj_wgt0, p1=Price1, q1=Adj_wgt1)

###############################
### compute Index Relatives ###
###############################
Daily_IXrel <- df2  %>% 
  ### Laspeyres, Paasche Index ###
  mutate(., L_IXrel = sum(q0*p1)/sum(q0*p0),  
         P_IXrel = sum(q1*p1)/sum(q1*p0)) %>%
  
  ### Geo-means Index ###
  mutate(., p1_over_p0 = p1/p0,
         p0q0 = p0*q0,
         s0 = p0q0 / sum(p0q0),
         G_IXrel = prod((p1_over_p0)^s0)) %>% 
  
  ### Tornqvist Index ###
  mutate(., p1q1 = p1*q1,
         s1 = p1q1 / sum(p1q1),
         T_IXrel = prod((p1_over_p0)^((s0+s1)/2))) %>% 
  
  ### Fisher Index ###
  mutate(., F_IXrel = sqrt(L_IXrel*P_IXrel)) %>%
  
  ### Unwighted Price Index ###
  mutate(., Unwgt_IXrel = sum(p1)/sum(p0)) %>%
  
  ### Average Price Index ###
  mutate(., AvePrc = round(mean(current_price$Price1), digits=2)) %>%
  select(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date1, Day1) %>%
  distinct(., L_IXrel, P_IXrel, G_IXrel, F_IXrel, T_IXrel, Unwgt_IXrel, AvePrc, Date1, Day1)


#####################
### compute Index ###
#####################
Daily_IX_Adj <- Daily_IXrel %>%
  mutate(L_IX=round((L_IXrel-1)*100, digits=3), 
         P_IX=round((P_IXrel-1)*100, digits=3), 
         G_IX=round((G_IXrel-1)*100, digits=3),
         F_IX=round((F_IXrel-1)*100, digits=3),
         T_IX=round((T_IXrel-1)*100, digits=3),
         Unwgt_IX=round((Unwgt_IXrel-1)*100, digits=3),
         IX_type="Popularity_Adj_Proxy_wgt", n_matched=nrow(df2))


##############################
### Append 2 type of Index ###
##############################
Daily_IX <- rbind(Daily_IX_0, Daily_IX_proxy, Daily_IX_Adj)
Daily_IX
```


### Save Base Period Data
```{r}
data_index <- Daily_IX
save(data_index, file="S:/SURV727_Fundamental_Computing_DataDisplay/Final_Project/Amazon/Data/data_index.Rda")
```


### Keep Price Change Data for each laptop for data visualization

```{r}
data_PC <- df %>% drop_na(PriceChange)  %>%
  select("Product_Name", "PriceChange", "PriceChange_prct", "Count_Review1", "Count_Review0", "Date1","Day1")
data_PC
```


### Save Base Period Data
```{r}
save(data_PC,file="S:/SURV727_Fundamental_Computing_DataDisplay/Final_Project/Amazon/Data/data_PC.Rda")
```

